%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{deedy-resume} % Use US Letter paper (letterpaper), change to a4paper for A4

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Eloise Macdonald-Meyer}{Ducky}{ % Your name
\urlstyle{same}\url{http://debarghyadas.com} \\ % Your website, LinkedIn profile or other web address
\href{mailto:ducky@fastmail.com}{ducky@fastmail.com} | +44 74 038 944 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\subsection{RMIT}

\descript{Bachelor of Technology}
\location{Expected Feb 2018 | Melbourne, AUS}
\descript{Previously B.Sc & B.Comp at University of Tasmania}
\location{Hobart, AUS}
Previous Majors in Games Technology and Geographic Information Systems \\
President of the UTAS Computing Society \\
Marketing and Sponsorship Manager for UTAS Robogals \\
Presenter at Edge Radio \\
IEEE student chapter founder \\
Treasurer of TAMS \\
Delegate and Guide for White Water Rafting Club \\
PC and Handheld Coordinator for DigiVisiPop \\

\sectionspace % Some whitespace after the section


%------------------------------------------------

\subsection{University of South Australia}

\location{Summer 2016 | Adelaide, AUS}
Attended the 2016 Augmented Reality (AR) Summer School, co-run with DAQRI. \\
Introduction to ARtoolkit and other techniques and research areas of AR. \\
Started Escher/Puzzle Cube Project \\

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{The Friends' School}

\location{Grad. Dec 2010 | Hobart, AUS}
English, Science, Philosophy, Maths, Japanese \\
Distinctions in National Maths and Science challenges \\
1st Women's Badminton, Hockey and Orienteering Teams \\
Marimba Ensemble, 2nd in National Percussion Eisteddfod \\
Jazz Band and Orchestra, Percussion and Clarinet \\
Sound and Lightning Technician for Drama, Ceramic Club \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links/Orgas and volunteering
%------------------------------------------------

\section{Volunteering}

\location{Organisation Role}
Tasjam | Founder \textbullet{} Startup Tas | Committee \textbullet{} TUCS | President \textbullet{} \\
ACS | Committee/YiTtas Chair \textbullet{} Girl Geek Coffees | Ambassador \\
linux.conf.au | Organiser \textbullet{} CompCon | Co-Founder \\
Robogals | Sponsorship and marketing manager \textbullet{} Django Girls \\
\location{Volunteer}
PAXaus \textbullet{} Surprise Attack \textbullet{} GCAP \textbullet{} Unite \\
pyconau \textbullet{} kiwipycon \textbullet{} BuzzConf  \\


%\section{Links}

%Github:// \href{https://github.com/duckytape}{\bf duckytape} \\
%LinkedIn:// \href{https://www.linkedin.com/in/eloiseducky}{\bf eloiseducky} \\
%Twitter:// \href{https://twitter.com/ducky_tape}{\bf @ducky_tape} \\
%Gitbook:// \href{https:duckytape.gitbooks.io//}{\bf duckytape} \\

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework / Presentations
%------------------------------------------------

\section{Presentations}

\begin{tabular}{rll}
2017 & Nz.js conf & Augmenting Reality with JavaScript\\
2016 & OSCONeu & I just want to talk about wagtail and how great it is\\
2016 & BuzzConf & ARgh: Not so real monsters!\\
2016 & Pyconau & Mental Health in Development\\
{\footnotesize \textit{\textbf{Panels}}} \\
2016 & PAXaus & Panel: My Friends keep leaving and it's ruining boardgames day\\
\end{tabular}

\sectionspace % Some whitespace after the section

%------------------------------------------------

%\subsection{Graduate}

%Advanced Machine Learning \\
%Open Source Software Engineering \\
%Advanced Interactive Graphics \\
%Compilers + Practicum \\
%Cloud Computing

%\sectionspace % Some whitespace after the section

%------------------------------------------------

%\subsection{Undergraduate}

%Information Retrieval \\
%Operating Systems \\
%Artificial Intelligence + Practicum \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
%Unix Tools and Scripting

%\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Most used:}
Python {\footnotesize \textit{\textbf{(esp. Django \& WagtailCMS)}}} \textbullet{} HTML/Jinja \textbullet{} CSS/SCSS \\
C \textbullet{} \LaTeX\ \textbullet{} Java \\
\location{Experimenting:}
JavaScript {\footnotesize \textit{\textbf{(esp. AR.js, tracking.js, Aframe)}}} \textbullet{} C++ \textbullet{} C# \textbullet{} Swift \\
\location{Other Tools:}
Unity3D \textbullet{} Xcode \textbullet{} Android studio \textbullet{} ArcGIS/QGIS \\
Emacs \textbullet{} vim \textbullet{} Wordpress \\

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Takeflight}
\descript{| Web Applications Engineer}

\location{March 2015 – July 2017 | Hobart, AUS}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item worked with a small team in many areas of development; from breaking down the design into the back end, and staying true to it in front end. Testing everything thoroughly before and after deployment. \\
\item Started the development of documentation for internal tools as well as documentation and support for clients. \\
\item Promoted takeflight and it's work through conference attendance and talks on open source tools. \\
\item Main technology used: Django (python) \textbullet{} Wagtail (CMS) \textbullet{} Node.js \textbullet{} scss & jinja \\
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{University of Tasmania}
\descript{| Telephony Technician}

\location{May 2014 – January 2015 | Hobart, AUS}
\begin{tightitemize}
\item Provided Telephony support across all UTAS campuses, including interstate locations. Support included, but was not limited to: Repairing and refitting DECT and Ericsson desk phones \textbullet{} Node Room Maintenance \textbullet{} Client liason and customer service \textbullet{} Testing and cleaning of all telephony equipment \\
\item Inventory Management of all telephony equipment, including receiving and unpacking new hardware. \\
\item Database Management of many internal databases including tracking of billing and management of address books.\\
\item Some technology used: Unix \\
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Python in Schools Workshop}
\descript{| Founder}

\location{March 2014 | Tasmania, Australia}
\begin{tightitemize}
\item Created online resources for teaching children from grade 3 onwards about computers and coding. \\
\item Created modular sprite based game in python using pygame. This was to be used and modified by participants and was thus well documented readable.\\
\item Liased with schools and other family oriented organisations to host workshops. \\
\item Recruited and trained volunteers to be mentors and help in these workshops \\
\item Technology used: Gitbook \textbullet{} Python \textbullet{} Pygame \\
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Projects
%------------------------------------------------

\section{Projects}

\runsubsection{Binnable}
\descript{| Captain}

\location{Nov 2016 | Santa Cruz, CA}
After pitching a mobile application that used computer vision to educate and gamify recycling, Binnable (then unnamed) was selected as one of the top 10 ideas for the weekend. A team was then successfully assembled to research and prototype the application. A pitch was polished and delivered at the end of 48 hours.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Puzzle Cube}
\descript{| Game Designer and Technical Writer}

\location{February 2016 | Adelaide, AUS}
For the end of the augmented reality summer school a final project was made in a team of three. The puzzle cube was a physical cube with markers on each side and was originally designed to have escher like puzzles augmented inside the cube. However by the delivery of this project it had extended to have many different games augmented onto the cube.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{AirCondor}
\descript{| Frontend Developer and Map Wrangler}

\location{July 2015 | Hobart, AUS}
An air conditioner recommendation application using the air conditioner cooling data and energy rating for air conditioners. A team of four found and processed the data before giving it an easy to use, responsive, and queryable frontend

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{What is Gov?}
\descript{| Data Wrangler}

\location{July 2014 | Hobart, AUS}
A game for iOS. Created using the list of Commonwealth Government Agencies and Functions, the game is designed to educate players about the agencies and roles of the Australian Government in a fun multiplayer environment.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Marvellous Ultimate Appliance}
\descript{| Visual Designer, Game Designer}

\location{May 2013 | Hobart, AUS}
Marvellous Ultimate Appliance is an electronic card game designed to help raise awareness of the energy consumed by common household appliances. Drawing on the data provided by the E3 Program (http://www.energyrating.gov.au), the game is inspired by popular battle card games such as “Magic: The Gathering”; the data is used to provide stats for cards, representing each appliance in the E3 Program database.
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards}

\begin{tabular}{rll}
2016	 & APAC & Google WTM/Anita Borg Memorial Scholar\\
2016	 & Australia & Start Up Catalyst Youth Mission Recipient \\
2016	 & Worldwide & Xbox Game Changer for GDC'17\\
2015	 & Tasmania & Most Commercially Viable Project, Govhack\\
2014	 & Aus and NZ & Govhack Best Use of National Archives of Australia Data \\
2014	 & Aus and NZ & Govhack Best Open Government Data Hack \\
2014	 & Aus and NZ & Govhack 2\textsuperscript{nd} Best Digital Humanities Hack \\
2013	 & Aus and NZ & Govhack Best Use of data.gov.au \\
\end{tabular}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Presentations
%------------------------------------------------

%\section{Presentations}

%\begin{tabular}{rll}
%2017 & Nz.js conf & Augmenting Reality with JavaScript\\
%2016 & OSCONeu & I just want to talk about wagtail and how great it is\\
%2016 & BuzzConf & ARgh: Not so real monsters!\\
%2016 & Pyconau & Mental Health in Development\\
%2016 & PAXaus & Panel: My Friends keep leaving and it's ruining boardgames day\\
%\end{tabular}

%\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
